A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
A few examples for scopes

%%In package \emph{gamlss::get.K} function \c{get.K} evaluates its expression in its
%%parent environment, the one of the body of \c{get.K} returned from
%%\c{environment()}.
%%
%%\begin{lstlisting}
%%eval(parse(text = paste(\"fam$dld\", ii, sep = \"\")), envir = environment())
%%\end{lstlisting}
%%
%%
%%The \emph{glue} library is used to interpolate string litterals with variables, such as in \c{glue('My name is \{name\}.')} where \c{name} will be subtituted by its value. \emph{glue} makes it possible to define transformers that process those interpolated variables. They are built upon the \c{identity_transformer}, which uses \eval. The interpretation environment for \eval is often global here, as the string litterals are often used to print variabels at the top level.
%%
%%\begin{lstlisting}
%%identity_transformer <- function(text, envir) 
%%{
%%    eval(parse(text = text, keep.source = FALSE), envir)
%%}
%%\end{lstlisting}
%%
%%
%%The \c{imchange} function of package \c{imager} makes it possible to modify images using a dedicated formula syntax using \c{\~}.\footnote{Inspired by \c{map} in package \emph{purr}.}  Here, \eval is evaluated in \c{newenv}, which creates a new environment that inherits from \c{parent.frame()} by default. We classify it as 1+.
%%
%%
%%\begin{lstlisting}
%%newenv <- new.env()
%%...
%%fo <- parse(text=as.character(fo)[2])
%%im[where] <- eval(fo,envir=newenv,enclos=env)
%%\end{lstlisting}
%%
%%\c{adjCoef} in package \emph{actuar} find the root of an equation defined by a function \c{h} whose arguments must be named \c{x} and \c{y}.
%%\c{h} is transformed into an auxiliary function \c{h2} that can be optimized. Here, the list used for \c{envir} ensures the correspondance between the textual arguments of \c{h} and the arguments of \c{h2}. 
%%
%%
%%\begin{lstlisting}
%%sh <- substitute(h)
%%fcall <- paste(sh, "(x, y)")
%%...
%%h2 <- function(x, y)
%%    eval(parse(text = fcall),
%%    envir = list(x = x, y = y),
%%    enclos = parent.frame(2))
%%\end{lstlisting}

>>>>

%%In package \emph{gamlss::get.K} function \c{get.K} evaluates its expression in its
%%parent environment, the one of the body of \c{get.K} returned from
%%\c{environment()}.
%%
%%\begin{lstlisting}
%%eval(parse(text = paste(\"fam$dld\", ii, sep = \"\")), envir = environment())
%%\end{lstlisting}
%%
%%
%%The \emph{glue} library is used to interpolate string litterals with variables, such as in \c{glue('My name is \{name\}.')} where \c{name} will be subtituted by its value. \emph{glue} makes it possible to define transformers that process those interpolated variables. They are built upon the \c{identity_transformer}, which uses \eval. The interpretation environment for \eval is often global here, as the string litterals are often used to print variables at the top level.
%%
%%\begin{lstlisting}
%%identity_transformer <- function(text, envir) 
%%{
%%    eval(parse(text = text, keep.source = FALSE), envir)
%%}
%%\end{lstlisting}
%%
%%

The \c{imchange} function of package \c{imager} makes it possible to modify images using a dedicated formula syntax using \c{\~}.\footnote{Inspired by \c{map} in package \emph{purr}.}  Here, \eval is evaluated in \c{newenv}, which creates a new environment that inherits from \c{parent.frame()} by default (classified as 1+).

\begin{lstlisting}
newenv <- new.env()
...
fo <- parse(text=as.character(fo)[2])
im[where] <- eval(fo,envir=newenv,enclos=env)
\end{lstlisting}

\c{adjCoef} in package \emph{actuar} find the root of an equation defined by a function \c{h} whose arguments must be named \c{x} and \c{y}.
\c{h} is transformed into an auxiliary function \c{h2} that can be optimized. Here, the list used for \c{envir} ensures the correspondance between the textual arguments of \c{h} and the arguments of \c{h2}.

\begin{lstlisting}
sh <- substitute(h)
fcall <- paste(sh, "(x, y)")
...
h2 <- function(x, y)
    eval(parse(text = fcall),
    envir = list(x = x, y = y),
    enclos = parent.frame(2))
\end{lstlisting}
